Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
passive

Now that the need for transparency about the inductive process has been established, a few more technical details can be droped to clarify what we have to make transparent.
It bears repeating that making public what has been done is not enough.
Merely showing the inductive results instead of the process that generated them is insufficient to appraise the theory.
On a conceptual level, we want to compare the following:
\begin{equation}
\mathcal{L}(\text{Theory}, \text{Reality})
\end{equation}

Where $\mathcal{L}$ stands for the loss function, i.e., how to compare predictions and reality.
To allow for induction, we replace theory with a model (not necessarily a statistical one) or, put differently, a multitude of implications about the data from the theory.

>>>>

Now that the need for transparency about the inductive process has been established, a few more technical details can be droped to clarify what we have to make transparent.
It bears repeating that making public what has been done is not enough.
Merely showing the inductive results instead of the process that generated them is insufficient to appraise the theory.
On a conceptual level, the following has to be compared:
\begin{equation}
\mathcal{L}(\text{Theory}, \text{Reality})
\end{equation}

Where $\mathcal{L}$ stands for the loss function, i.e., how to compare predictions and reality.
To allow for induction, the theory gets replaced with a model (not necessarily a statistical one) or, put differently, a multitude of implications about the data from the theory.
